---
title: "Lab 2 Solutions"
author: ""
date: ""
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    df_print: paged
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

## Shell command

In this repo is a zip file named `organize_me.zip`. It can by unzipped by
running `unzip("organize_me.zip")`. Do this in your console so you only unzip
the folder once and not each time you knit the Rmd file.

The files in `organize_me/` contain a sample of various files you may have if 
you run a simulation on a high performance computer. Although, they are
currently disorganized. Organize the contents in `organize_me/` using the 
command line according to the following steps.

1. delete all `.input2` files.
2. remove the `flags/` directory and all of its contents.
3. place the test data text files in a directory named `test_data/`.
4. place the `.sh` files in a directory named `scripts_shell/`.
5. place the `.R` files in a directory named `scripts_R/`.
6. place the `.qsub` files in a directory named `hpc_start/`.
7. copy directory `organize_me/` and name the copy `simulations/`.
8. delete directory `organize_me/` and all of its contents.

```{bash eval=FALSE}
# assuming you are in organize_me/
rm *.input2

rm -rf flags/

mkdir test-data/
mv testdata*.txt test-data/

mkdir shell-scripts/
mv *.sh shell-scripts/

mkdir R-scripts/
mv *.R R-scripts/

mkdir hpc-run/
mv *.qsub hpc-run/

cd ../
cp organize_me/ simulation/

rm -rf organize_me/
```


## Attributes

Create a date-time object based on the atomic double vector below. You'll
need to set the class attribute to `"POSIXct"`

```{r}
z <- seq(0, 3600 * 10, by = 3600)
```

```{r}
attr(z, which = "class") <- "POSIXct"
z
```


What do you notice about the date-time? If you are unsure, check out
Unix Epoch.

## Subsetting

Consider the atomic vector `x`.

```{r}
set.seed(0826) # set seed to ensure reproducibility
x <- sample(x = c(letters, -15:15), size = 50, replace = TRUE)
x
```

1. subset only the letters from `x`.

```{r}
x[x %in% letters]
```

2. subset only the negative numbers from `x`.

```{r}
y <- as.numeric(x)
x[y < 0 & !is.na(y)]
```

3. select the numbers divisible by 3 from `x`.

```{r}
x[as.numeric(x) %% 3 == 0 & !is.na(y)]
```

4. remove all values with an even index from `x`.

```{r}
x[-2 * (1:(length(x) / 2))]
```

